---
title: "Teach Me How to Google"
subtitle: "MEDS 2021-22"
author: "Sam Csik"
date: "October 11th, 2021"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width = 9, fig.height = 3.5, fig.retina = 3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include = FALSE, warning = FALSE}
# load package
library(xaringanthemer)

# set accent theme
style_mono_accent(
  header_font_google = google_font("Sanchez"), 
  text_font_google = google_font("Glacial Indifference", "300", "300i"),
  code_font_google = google_font("Fira Mono"),
  base_color = "#05859B",
  white_color = "#93C6C2",
  background_color = "#FFFFFF",
  header_font_weight = 400,
  header_h1_font_size = "2.25rem",
  header_h2_font_size = "1.75rem",
  header_h3_font_size = "1.5rem",
  footnote_font_size = "0.7em",
)
```

## Some Intro stuff

we all need help with our code -- whether it's figuring out if there's a function that does what we want or trying to troubleshoot a pesky error message. No one is exempt from this (show tweets)

---
## General approaches (non-error)

---
## General apporaches (error message)

1.  check the easy things (have a check list)
2.  run line by line (if pipes)

---
## Easy things to check

spelling, commas, etc.

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Debugging can be frustrating for our first time <a href="https://twitter.com/hashtag/RStats?src=hash&amp;ref_src=twsrc%5Etfw">#RStats</a> students... but maybe it can lead to a spot on Debugging Bingo! DeBug-o? DeBingo? <br><br>Here&#39;s a copy if you want to include the common errors you see in your class!<a href="https://t.co/mI3g2QfvR2">https://t.co/mI3g2QfvR2</a> <a href="https://t.co/kyOCO3jjzL">pic.twitter.com/kyOCO3jjzL</a></p>&mdash; Dr. Ji Son (@cogscimom) <a href="https://twitter.com/cogscimom/status/1354508785365078016?ref_src=twsrc%5Etfw">January 27, 2021</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

---
## Isolate the problem (line-by-line)

---

## General "How to query Google"

insert schematics here

---

## Ways to write good, eas(ier) to debug code

use explaining variables!
<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Great post on why &quot;explaining variables&quot; and &quot;explaining functions or methods&quot; are better than code comments.<br><br>I found that my enthusiasm for writing/maintaining comments peaked many years ago and I&#39;m better off using other techniques to make the non-obvious (more) obvious. <a href="https://t.co/yIIOnd8qHz">https://t.co/yIIOnd8qHz</a></p>&mdash; Jenny Bryan (@JennyBryan) <a href="https://twitter.com/JennyBryan/status/1412140590842597385?ref_src=twsrc%5Etfw">July 5, 2021</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>


